Analyses

### 2022-07-25 analyses.RmD
- major updates for revision - included multiple imputation - changed theory - include new data-set - extended discussion

---
title: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache = F)
options(digits = 3, width = 250, scipen=999)
```

Here you can find the code and the results of all analyses. To see the code, click on button "Code". Alternatively, you can download the rmd file from the github repo.

@@

```{r r-setup, results='hide', cache=FALSE}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

@@

```{r}
find_var <- function(name, data = doc)(
  # finds the variables names for an item for each wave
    data %>% 
    filter(Label == name) %>% 
    select(variable) %>% 
    unlist() %>% 
    set_names(sub("\\_.*", "", .))
)
```

@@

  if(isTRUE(class(data_aff_neg) == "lmerModLmerTest")) {
         dat_fig_results <- 
           broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
           mutate(dv = "aff_neg") %>% 
           rbind(
             broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
               mutate(dv = "aff_pos")) %>% 
           rbind(
             broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
               mutate(dv = "life_sat"))
         } else{ 
           dat_fig_results <- 
             data_aff_neg %>% 
             mutate(dv = "aff_neg") %>% 
             rbind(data_aff_pos %>% 
                   mutate(dv = "aff_pos")) %>% 
             rbind(data_life_sat %>% 
                     mutate(dv = "life_sat")) %>% 
           rename(conf.low = `2.5 %`, conf.high = `97.5 %`)
           }
  dat_fig_results %<>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect")),
    analysis = analysis
  ) %>% 
  select(dv, iv, type, analysis, estimate, conf.low, conf.high, p.value)

  # select Social Media type of activity
  if(type == "activity") {
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_read", "soc_med_like_share", "soc_med_post")) %>% 
    mutate(
      iv = factor(.$iv, 
                  levels = c("soc_med_post", "soc_med_like_share", "soc_med_read"), 
                  labels = c("Posting", "Liking & Sharing", "Reading"))
    )
  } else if(type == "channels"){
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")) %>% 
    mutate(iv = factor(.$iv, levels = c("soc_med_yt", "soc_med_wa", "soc_med_ig", "soc_med_tw", "soc_med_fb"), labels = c("YouTube", "WhatsApp", "Instagram", "Twitter", "Facebook")))
  } else if(type == "control"){
    dat_fig_results %<>%
      filter(iv %in% c("male", "health", "loc_cntrl_int_m", "employment_facPublic service", "act_spo", "sat_dem")) %>% 
      mutate(iv = factor(.$iv, levels = c("male", "health", "loc_cntrl_int_m", "employment_facPublic service", "act_spo", "sat_dem"), 
                         labels = c("Male", "Health", "Internal locus of control", "Employed public service", "Sport", "Satisfaction democracy")))
  }
  return(dat_fig_results)
}

@@

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("grey40", "deepskyblue", "darkcyan", "cornflowerblue", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = analysis),
                lwd = .75, height = .2, position = position_dodge(.5)) +
  geom_point(aes(color = analysis), size = 2, position = position_dodge(.5)) +
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
    theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  guides(colour = guide_legend(reverse=T)) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

@@

# Data Wrangling

```{r}
doc <- read_csv("documentation/10094_vi_de_v4_0.csv")
d_raw <- read_csv("data/10094_da_de_v4_0.csv")
```

@@

```{r}
# identify variable names of items, using custom function
health <- find_var("Gesundheitszustand") # wsn't collected at wave 21
aff_neg_1 <- find_var("Depressivitaet: einsam")
aff_neg_2 <- find_var("Depressivitaet: aergerlich")
aff_neg_3 <- find_var("Depressivitaet: so niedergeschlagen")
aff_neg_4 <- find_var("Depressivitaet: sehr nervoes")
aff_neg_5 <- find_var("Depressivitaet: aengstlich")
aff_neg_6 <- find_var("Depressivitaet: bedrueckt und traurig")
aff_pos_1 <- find_var("Depressivitaet: ruhig und gelassen")
aff_pos_2 <- find_var("Depressivitaet: gluecklich")
aff_pos_3 <- find_var("Depressivitaet: voller Energie")
act_wrk <- find_var("Zuhause verlassen: Arbeit")
act_spo <- find_var("Zuhause verlassen: Sport")
act_frn <- find_var("Zuhause verlassen: Freunde oder Verwandte treffen")
act_sho <- find_var("Zuhause verlassen: Essen einkaufen")
act_pet <- find_var("Zuhause verlassen: Haustier ausfuehren")
sat_dem <- find_var("Demokratiezufriedenheit: Oesterreich")
work_h <- find_var("Arbeitsstunden: Jetzt pro Woche")
work_homeoff <- find_var("Aenderung berufliche Situation: Home-Office")
hh_income <- find_var("Aktuelles Haushaltseinkommen")
med_txt_kro <- find_var("Mediennutzung: Kronen Zeitung oder www.krone.at")
med_txt_sta <- find_var("Mediennutzung: Der Standard oder derstandard.at")
med_txt_pre <- find_var("Mediennutzung: Die Presse oder diepresse.com")
med_txt_oes <- find_var("Mediennutzung: Oesterreich oder oe24.at")
med_txt_kur <- find_var("Mediennutzung: Kurier oder kurier.at")
med_txt_slz <- find_var("Mediennutzung: Salzburger Nachrichten oder salzburg.at")
med_txt_son <- find_var("Mediennutzung: Sonstige oesterreichische Tageszeitungen")
med_vid_orf <- find_var("Mediennutzung: ORF (Nachrichten)")
med_vid_pri <- find_var("Mediennutzung: Privatfernsehen (Nachrichten)")
soc_med_fb <- find_var("Soziale Medien: Facebook")
soc_med_tw <- find_var("Soziale Medien: Twitter")
soc_med_ig <- find_var("Soziale Medien: Instagram")
soc_med_yt <- find_var("Soziale Medien: Youtube")
soc_med_wa <- find_var("Soziale Medien: WhatsApp")
soc_med_read <- find_var("Soziale Medien Aktivitaet: Postings zu Corona anderer lesen")
soc_med_like_share <- find_var("Soziale Medien Aktivitaet: Postings liken, teilen oder retweeten")
soc_med_post <- find_var("Soziale Medien Aktivitaet: selber Postings zu Corona verfassen")
life_sat <- find_var("Lebenszufriedenheit")
risk_prop <- find_var("Risikobereitschaft")
loc_cntrl_int_1 <- find_var("Psychologie: habe Leben selbst in der Hand")
loc_cntrl_int_2 <- find_var("Psychologie: Belohnung durch Anstrengung")
loc_cntrl_int_3 <- find_var("Psychologie: Fremdbestimmung")
loc_cntrl_int_4 <- find_var("Psychologie: Schicksal")
```

Select variables.

```{r}
d_wide <- d_raw %>% 
  select(
    id = RESPID,
    gender = SD_GENDER,
    acc_bal = SD_ACCESS_BALCONY,
    acc_gar = SD_ACCESS_GARDEN,
    year_birth = SD_BIRTHYEAR,
    born_aus = SD_BORN_AUSTRIA,
    born_aus_prnts = SD_MIGR_BACKGR,
    county = SD_BULA,
    edu = SD_EDU,
    employment = SD_EMPLSTATUS_FEB2020,
    hh_adults = SD_HH_ADULTS,
    hh_child18 = SD_HH_CHILD18,
    hh_child17 = SD_HH_TEENS,
    hh_child14 = SD_HH_CHILD14,
    hh_child5 = SD_HH_CHILD5,
    hh_child2 = SD_HH_CHILD2,
    hh_oldfam = SD_HH_OLDERFAM,
    hh_outfam = SD_HH_OUTERFAM,
    hh_partner = SD_HH_PARTNER,
    # hh_income = SD_HHINCOME_FEB2020,
    home_sqm = SD_HOME_SQM,
    home_owner = SD_HOMEOWNER,
    # work_h = SD_WORKHOURS_FEB2020,
    health = all_of(health),
    life_sat = all_of(life_sat),
    aff_neg_1 = all_of(aff_neg_1),
    aff_neg_2 = all_of(aff_neg_2),
    aff_neg_3 = all_of(aff_neg_3),
    aff_neg_4 = all_of(aff_neg_4),
    aff_neg_5 = all_of(aff_neg_5),
    aff_neg_6 = all_of(aff_neg_6),
    aff_pos_1 = all_of(aff_pos_1),
    aff_pos_2 = all_of(aff_pos_2),
    aff_pos_3 = all_of(aff_pos_3),
    act_wrk = all_of(act_wrk),
    act_spo = all_of(act_spo),
    act_frn = all_of(act_frn),
    act_sho = all_of(act_sho),
    act_pet = all_of(act_pet),
    sat_dem = all_of(sat_dem),
    sat_dem = all_of(sat_dem),
    work_h = all_of(work_h),
    work_homeoff = all_of(work_homeoff),
    hh_income = all_of(hh_income),
    med_txt_kro = all_of(med_txt_kro),
    med_txt_sta = all_of(med_txt_sta),
    med_txt_pre = all_of(med_txt_pre),
    med_txt_oes = all_of(med_txt_oes),
    med_txt_kur = all_of(med_txt_kur),
    med_txt_slz = all_of(med_txt_slz),
    med_txt_son = all_of(med_txt_son),
    med_vid_orf = all_of(med_vid_orf),
    med_vid_pri = all_of(med_vid_pri),
    soc_med_fb = all_of(soc_med_fb),
    soc_med_tw = all_of(soc_med_tw),
    soc_med_ig = all_of(soc_med_ig),
    soc_med_yt = all_of(soc_med_yt),
    soc_med_wa = all_of(soc_med_wa),
    soc_med_like_share = all_of(soc_med_like_share),
    soc_med_read = all_of(soc_med_read),
    soc_med_post = all_of(soc_med_post),
    risk_prop = all_of(risk_prop),
    loc_cntrl_int_1 = all_of(loc_cntrl_int_1),
    loc_cntrl_int_2 = all_of(loc_cntrl_int_2),
    loc_cntrl_int_3 = all_of(loc_cntrl_int_3),
    loc_cntrl_int_4 = all_of(loc_cntrl_int_4)
  )
```

@@

```{r}
doc_selected <- filter(doc, variable %in% c(
  "RESPID",
  "SD_GENDER",
  "SD_ACCESS_BALCONY",
  "SD_ACCESS_GARDEN",
  "SD_BIRTHYEAR",
  "SD_BORN_AUSTRIA",
  "SD_MIGR_BACKGR",
  "SD_BULA",
  "SD_EDU",
  "SD_EMPLSTATUS_FEB2020",
  "SD_HH_ADULTS",
  "SD_HH_CHILD18",
  "SD_HH_TEENS",
  "SD_HH_CHILD14",
  "SD_HH_CHILD5",
  "SD_HH_CHILD2",
  "SD_HH_OLDERFAM",
  "SD_HH_OUTERFAM",
  "SD_HH_PARTNER",
  "SD_HHINCOME_FEB2020",
  "SD_HOME_SQM",
  "SD_HOMEOWNER",
  "SD_WORKHOURS_FEB2020",
  health[1],
  life_sat[1],
  aff_neg_1[1],
  aff_neg_2[1],
  aff_neg_3[1],
  aff_neg_4[1],
  aff_neg_5[1],
  aff_neg_6[1],
  aff_pos_1[1],
  aff_pos_2[1],
  aff_pos_3[1],
  act_wrk[1],
  act_spo[1],
  act_frn[1],
  act_sho[1],
  act_pet[1],
  sat_dem[1],
  work_h[1],
  work_homeoff[1],
  hh_income[1],
  med_txt_kro[1],
  med_txt_sta[1],
  med_txt_pre[1],
  med_txt_oes[1],
  med_txt_kur[1],
  med_txt_slz[1],
  med_txt_son[1],
  med_vid_orf[1],
  med_vid_pri[1],
  soc_med_fb[1],
  soc_med_tw[1],
  soc_med_ig[1],
  soc_med_yt[1],
  soc_med_wa[1],
  soc_med_like_share[1],
  soc_med_post[1],
  soc_med_read[1],
  risk_prop[1],
  loc_cntrl_int_1[1],
  loc_cntrl_int_2[1],
  loc_cntrl_int_3[1],
  loc_cntrl_int_4[1]
  ))
```

Recode variables.

@@

Make data from wide to long.

```{r}
d_long <-
  d_wide %>% 
  pivot_longer(
    cols = health...W1:loc_cntrl_int_4...W9,
    names_to = "item",
    values_to = "value"
  ) %>% 
  separate(item, c("item", "wave"), sep = "\\.\\.\\.", extra = "merge") %>% 
  pivot_wider(names_from = "item", values_from = "value")
```

Recode values.

@@

Order dataset. First id, then wave.

```{r}
d_long %<>%
  arrange(id, wave)
```

# Impute data

Determine amount of missingness per respondent per wave. Because calculation takes long, this chunk is not executed but loaded from memory. To execute, set eval == TRUE.

```{r eval=TRUE, cache=TRUE}
vars_used <- c("life_sat", "aff_pos_1", "aff_pos_2", "aff_pos_3", "aff_neg_1", "aff_neg_2", "aff_neg_3", "aff_neg_4", "aff_neg_5", "aff_neg_6", "soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw", "age", "male", "born_aus", "born_aus_prnts", "edu_fac", "employment_fac", "health", "res_vienna", "acc_bal", "acc_gar", "home_sqm", "med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri", "risk_prop", "loc_cntrl_int_1", "loc_cntrl_int_2", "loc_cntrl_int_3", "loc_cntrl_int_4", "act_wrk", "act_spo", "act_frn", "act_sho", "act_pet", "sat_dem")

# filter respondents with more than 50% missing data
d_long_filt <- 
  d_long %>% 
  mutate(na_perc = rowSums(is.na(select(., all_of(vars_used))) / ncol(select(., all_of(vars_used))))) %>% 
  filter(na_perc < .5)

>>>>

---
title: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache=T, rows.print=20)
options(digits=2, width=260, scipen=999)
```

 - Here you can find the code and the results of all analyses. 
 - To see the code, click on button "Code". A
 - Alternatively, you can download the rmd file from the github repo.
 - The data are hosted on aussda. Please download them separately, to rerun the analyses (https://doi.org/10.11587/28KQNS). 
 - Note that this paper uses an advance version consisting of 32 waves, which is at the time of writing not officially published.

@@

```{r r-setup, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

@@

```{r}
find_var <- function(name, data = doc)(
  # finds the variables names for an item for each wave
    data %>%
    filter(Label == name) %>%
    select(Variable) %>%
    unlist() %>%
    set_names(sub("\\_.*", "", .))
)
# find_var <- function(name, data = doc)(
#   # finds the variables names for an item for each wave
#     data %>% 
#     filter(`Variable names (DE)` == name) %>% 
#     select(`VARNAME (CA)`) %>% 
#     unlist() %>% 
#     set_names(sub("\\_.*", "", .))
# )
```

@@

  if(isTRUE(class(data_aff_neg) == "lmerModLmerTest")) {
         dat_fig_results <- 
           broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
           mutate(dv = "aff_neg") %>% 
           rbind(
             broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
               mutate(dv = "aff_pos")) %>% 
           rbind(
             broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
               mutate(dv = "life_sat"))
         } else{ 
           dat_fig_results <- 
             data_aff_neg %>% 
             mutate(dv = "aff_neg") %>% 
             rbind(data_aff_pos %>% 
                   mutate(dv = "aff_pos")) %>% 
             rbind(data_life_sat %>% 
                     mutate(dv = "life_sat")) %>% 
           rename(conf.low = `2.5 %`, conf.high = `97.5 %`)
           }
  dat_fig_results %<>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect")),
    Analysis = analysis
  ) %>% 
  select(dv, iv, type, Analysis, estimate, conf.low, conf.high, p.value)

  # select Social Media type of activity
  if(type == "activity") {
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_read", "soc_med_like_share", "soc_med_post")) %>% 
    mutate(
      iv = factor(.$iv, 
                  levels = c("soc_med_post", "soc_med_like_share", "soc_med_read"), 
                  labels = c("Posting", "Liking & Sharing", "Reading"))
    )
  } else if(type == "channels"){
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")) %>% 
    mutate(iv = factor(.$iv, levels = c("soc_med_yt", "soc_med_wa", "soc_med_ig", "soc_med_tw", "soc_med_fb"), labels = c("YouTube", "WhatsApp", "Instagram", "Twitter", "Facebook")))
  } else if(type == "control"){
    dat_fig_results %<>%
      filter(iv %in% c("male", "health", "loc_cntrl_int_m", #"employment_facPublic service", 
                       "act_spo", "sat_dem")) %>% 
      mutate(iv = factor(.$iv, levels = c("male", "health", "loc_cntrl_int_m", #"employment_facPublic service", 
                                          "act_spo", "sat_dem"), 
                         labels = c("Male", "Health", "Internal locus of control", #"Employed public service", 
                                    "Sport", "Satisfaction democracy")))
  }
  return(dat_fig_results)
}

@@

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE, facet = "comm", title = NULL){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("black", "grey75", "darkcyan", "deepskyblue", "cornflowerblue", "darkcyan", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = Analysis),
                lwd = .75, height = .2, position = position_dodge(-.7)) +
  geom_point(aes(color = Analysis), size = 1.5, position = position_dodge(-.7)) +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 1)
    ) +
  {if(!is.null(title)) ggtitle(title)} +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  # guides(colour = guide_legend(reverse=T)) +
    {if(facet == "comm")
      facet_grid(rows = vars(comm),
             cols = vars(dv),
             scales = "free",
             space = "free_y")
    } + 
    {if(facet == "analysis")
      facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y")
    }
}
```

@@

# Data Wrangling
## Load data

```{r}
# doc <- read_csv("documentation/10094_vi_de_v4_0.csv")
doc <- read_csv2("data/Variable_List_w1-34.csv")
# doc <- read_csv("documentation/W1-32_ACPP_Variablelist_V20220601.csv")
# d_raw <- read_csv("data/10094_da_de_v4_0.csv")
# d_raw_test <- read_csv("data/10094_da_de_v4_0.csv")
d_raw <- read_csv("data/W1-32_ACPP_V20220601.csv")
```

## Find names

@@

```{r}
# identify variable names of items, using custom function
health <- find_var("Gesundheitszustand") # wsn't collected at wave 21
aff_neg_1 <- find_var("Depressivitaet: einsam")
aff_neg_2 <- find_var("Depressivitaet: aergerlich")
aff_neg_3 <- find_var("Depressivitaet: so niedergeschlagen")
aff_neg_4 <- find_var("Depressivitaet: sehr nervoes")
aff_neg_5 <- find_var("Depressivitaet: aengstlich")
aff_neg_6 <- find_var("Depressivitaet: bedrueckt und traurig")
aff_pos_1 <- find_var("Depressivitaet: ruhig und gelassen")
aff_pos_2 <- find_var("Depressivitaet: gluecklich")
aff_pos_3 <- find_var("Depressivitaet: voller Energie")
act_wrk <- find_var("Zuhause verlassen: Arbeit")
act_spo <- find_var("Zuhause verlassen: Sport")
act_frn <- find_var("Zuhause verlassen: Freunde oder Verwandte treffen")
act_sho <- find_var("Zuhause verlassen: Essen einkaufen")
act_pet <- find_var("Zuhause verlassen: Haustier ausfuehren")
sat_dem <- find_var("Demokratiezufriedenheit: Oesterreich")
work_h <- find_var("Arbeitsstunden: Jetzt pro Woche")
work_homeoff <- find_var("Aenderung berufliche Situation: Home-Office")
hh_income <- find_var("Aktuelles Haushaltseinkommen")
med_txt_kro <- find_var("Mediennutzung: Kronen Zeitung oder www.krone.at")
med_txt_sta <- find_var("Mediennutzung: Der Standard oder derstandard.at")
med_txt_pre <- find_var("Mediennutzung: Die Presse oder diepresse.com")
med_txt_oes <- find_var("Mediennutzung: Oesterreich oder oe24.at")
med_txt_kur <- find_var("Mediennutzung: Kurier oder kurier.at")
med_txt_slz <- find_var("Mediennutzung: Salzburger Nachrichten oder salzburg.at")
med_txt_son <- find_var("Mediennutzung: Sonstige oesterreichische Tageszeitungen")
med_vid_orf <- find_var("Mediennutzung: ORF (Nachrichten)")
med_vid_pri <- find_var("Mediennutzung: Privatfernsehen (Nachrichten)")
soc_med_fb <- find_var("Soziale Medien: Facebook")
soc_med_tw <- find_var("Soziale Medien: Twitter")
soc_med_ig <- find_var("Soziale Medien: Instagram")
soc_med_yt <- find_var("Soziale Medien: Youtube")
soc_med_wa <- find_var("Soziale Medien: WhatsApp")
soc_med_read <- find_var("Soziale Medien Aktivitaet: Postings zu Corona anderer lesen")
soc_med_like_share <- find_var("Soziale Medien Aktivitaet: Postings liken, teilen oder retweeten")
soc_med_post <- find_var("Soziale Medien Aktivitaet: selber Postings zu Corona verfassen")
life_sat <- find_var("Lebenszufriedenheit")
risk_prop <- find_var("Risikobereitschaft")
loc_cntrl_int_1 <- find_var("Psychologie: habe Leben selbst in der Hand")
loc_cntrl_int_2 <- find_var("Psychologie: Belohnung durch Anstrengung")
loc_cntrl_int_3 <- find_var("Psychologie: Fremdbestimmung")
loc_cntrl_int_4 <- find_var("Psychologie: Schicksal")
trst_media <- find_var("Vertrauen: ORF")
trst_police <- find_var("Vertrauen: Polizei")
trst_media <- find_var("Vertrauen: Parlament")
trst_hlthsec <- find_var("Vertrauen: Gesundheitswesen")
trst_gov <- find_var("Vertrauen: Bundesregierung")
trst_army <- find_var("Vertrauen: Bundesheer")
corona_pos <- c(
  find_var("Corona-Diagnose: Respondent"),
  find_var("Corona-Diagnose: Monat")
)
```

## Select variables

```{r}
d_wide <- d_raw %>% 
  select(
    id = RESPID,
    gender = SD_GENDER,
    acc_bal = SD_ACCESS_BALCONY,
    acc_gar = SD_ACCESS_GARDEN,
    year_birth = SD_BIRTHYEAR,
    born_aus = SD_BORN_AUSTRIA,
    born_aus_prnts = SD_MIGR_BACKGR,
    county = SD_BULA,
    edu = SD_EDU,
    employment = SD_EMPLSTATUS_FEB2020,
    hh_adults = SD_HH_ADULTS,
    hh_child18 = SD_HH_CHILD18,
    hh_child17 = SD_HH_TEENS,
    hh_child14 = SD_HH_CHILD14,
    hh_child5 = SD_HH_CHILD5,
    hh_child2 = SD_HH_CHILD2,
    hh_oldfam = SD_HH_OLDERFAM,
    hh_outfam = SD_HH_OUTERFAM,
    hh_partner = SD_HH_PARTNER,
    # hh_income = SD_HHINCOME_FEB2020,
    home_sqm = SD_HOME_SQM,
    home_owner = SD_HOMEOWNER,
    # work_h = SD_WORKHOURS_FEB2020,
    health = all_of(health),
    life_sat = all_of(life_sat),
    aff_neg_1 = all_of(aff_neg_1),
    aff_neg_2 = all_of(aff_neg_2),
    aff_neg_3 = all_of(aff_neg_3),
    aff_neg_4 = all_of(aff_neg_4),
    aff_neg_5 = all_of(aff_neg_5),
    aff_neg_6 = all_of(aff_neg_6),
    aff_pos_1 = all_of(aff_pos_1),
    aff_pos_2 = all_of(aff_pos_2),
    aff_pos_3 = all_of(aff_pos_3),
    act_wrk = all_of(act_wrk),
    act_spo = all_of(act_spo),
    act_frn = all_of(act_frn),
    act_sho = all_of(act_sho),
    act_pet = all_of(act_pet),
    sat_dem = all_of(sat_dem),
    sat_dem = all_of(sat_dem),
    work_h = all_of(work_h),
    work_homeoff = all_of(work_homeoff),
    hh_income = all_of(hh_income),
    med_txt_kro = all_of(med_txt_kro),
    med_txt_sta = all_of(med_txt_sta),
    med_txt_pre = all_of(med_txt_pre),
    med_txt_oes = all_of(med_txt_oes),
    med_txt_kur = all_of(med_txt_kur),
    med_txt_slz = all_of(med_txt_slz),
    med_txt_son = all_of(med_txt_son),
    med_vid_orf = all_of(med_vid_orf),
    med_vid_pri = all_of(med_vid_pri),
    soc_med_fb = all_of(soc_med_fb),
    soc_med_tw = all_of(soc_med_tw),
    soc_med_ig = all_of(soc_med_ig),
    soc_med_yt = all_of(soc_med_yt),
    soc_med_wa = all_of(soc_med_wa),
    soc_med_like_share = all_of(soc_med_like_share),
    soc_med_read = all_of(soc_med_read),
    soc_med_post = all_of(soc_med_post),
    risk_prop = all_of(risk_prop),
    loc_cntrl_int_1 = all_of(loc_cntrl_int_1),
    loc_cntrl_int_2 = all_of(loc_cntrl_int_2),
    loc_cntrl_int_3 = all_of(loc_cntrl_int_3),
    loc_cntrl_int_4 = all_of(loc_cntrl_int_4),
    trst_media = all_of(trst_media),
    trst_police = all_of(trst_police),
    trst_media = all_of(trst_media),
    trst_hlthsec = all_of(trst_hlthsec),
    trst_gov = all_of(trst_gov),
    trst_army = all_of(trst_army),
    corona_pos = all_of(corona_pos)
  )
```

@@

```{r}
doc_selected <- filter(doc, Variable %in% c(
  "RESPID",
  "SD_GENDER",
  "SD_ACCESS_BALCONY",
  "SD_ACCESS_GARDEN",
  "SD_BIRTHYEAR",
  "SD_BORN_AUSTRIA",
  "SD_MIGR_BACKGR",
  "SD_BULA",
  "SD_EDU",
  "SD_EMPLSTATUS_FEB2020",
  "SD_HH_ADULTS",
  "SD_HH_CHILD18",
  "SD_HH_TEENS",
  "SD_HH_CHILD14",
  "SD_HH_CHILD5",
  "SD_HH_CHILD2",
  "SD_HH_OLDERFAM",
  "SD_HH_OUTERFAM",
  "SD_HH_PARTNER",
  "SD_HHINCOME_FEB2020",
  "SD_HOME_SQM",
  "SD_HOMEOWNER",
  "SD_WORKHOURS_FEB2020",
  health[1],
  life_sat[1],
  aff_neg_1[1],
  aff_neg_2[1],
  aff_neg_3[1],
  aff_neg_4[1],
  aff_neg_5[1],
  aff_neg_6[1],
  aff_pos_1[1],
  aff_pos_2[1],
  aff_pos_3[1],
  act_wrk[1],
  act_spo[1],
  act_frn[1],
  act_sho[1],
  act_pet[1],
  sat_dem[1],
  work_h[1],
  work_homeoff[1],
  hh_income[1],
  med_txt_kro[1],
  med_txt_sta[1],
  med_txt_pre[1],
  med_txt_oes[1],
  med_txt_kur[1],
  med_txt_slz[1],
  med_txt_son[1],
  med_vid_orf[1],
  med_vid_pri[1],
  soc_med_fb[1],
  soc_med_tw[1],
  soc_med_ig[1],
  soc_med_yt[1],
  soc_med_wa[1],
  soc_med_like_share[1],
  soc_med_post[1],
  soc_med_read[1],
  risk_prop[1],
  loc_cntrl_int_1[1],
  loc_cntrl_int_2[1],
  loc_cntrl_int_3[1],
  loc_cntrl_int_4[1],
  trst_media[1],
  trst_police[1],
  trst_media[1],
  trst_hlthsec[1],
  trst_gov[1],
  trst_army[1],
  corona_pos[1]
  ))
write.csv(doc_selected, "data/variables_selected.csv")
```

## Recode variables

@@

## Make long data format

```{r cache=T}
d_long <-
  d_wide %>% 
  pivot_longer(
    cols = health...W1:corona_pos...W32,
    names_to = "item",
    values_to = "value"
  ) %>% 
  separate(item, c("item", "wave"), sep = "\\.\\.\\.", extra = "merge") %>% 
  pivot_wider(names_from = "item", values_from = "value")
```

## Recode values

@@

## Order dataset

```{r}
d_long %<>%
  arrange(id, wave)

# create backup bc comp takes long
d_long_backup <- d_long
```

## Impute data

Next we impute data. Note that the actual imputation below is deactivated and loaded from memory to save time.

### Prep

Determine amount of missingness per respondent per wave. Because calculation takes long, this chunk is loaded from memory.

```{r}
vars_used <- c("life_sat", "aff_pos_1", "aff_pos_2", "aff_pos_3", "aff_neg_1", "aff_neg_2", "aff_neg_3", "aff_neg_4", "aff_neg_5", "aff_neg_6", "soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw", "age", "male", "born_aus", "born_aus_prnts", "edu_fac", "employment_fac", "health", "res_vienna", "acc_bal", "acc_gar", "home_sqm", "med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri", "risk_prop", "loc_cntrl_int_1", "loc_cntrl_int_2", "loc_cntrl_int_3", "loc_cntrl_int_4", "act_wrk", "act_spo", "act_frn", "act_sho", "act_pet", "sat_dem", "trst_media", "trst_police", "trst_media", "trst_hlthsec", "trst_gov", "trst_army", "corona_pos") # only include vars measured at _all_ points
```
